Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2023-04-21 analysis/paper/paper.qmd
add sample size & cv plot

>>>>

###### regression of CV with sample size ####

# Calculate the CV for each group

cv_tcsa_site_ass_mis <- tcsa_site_ass_mis %>%
  dplyr::group_by(mis_stage) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

cv_tcsa_site_ass_mis$mis_stage <- factor(cv_tcsa_site_ass_mis$mis_stage, levels = c("Before", "LGM", "After"))

ggplot(cv_tcsa_site_ass_mis, aes(x = CV, y = sample_size, color = mis_stage)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each period")

### combine with raw material info ##

tcsa_site_ass_mis_raw <- tcsa_site_ass %>% 
                          left_join(tcsa_raw, by = "min_tcsa") %>% 
                      mutate(mis_stage = case_when (
                        age_ka > 26.5 ~ 'Before' , age_ka > 19 ~ 'LGM', age_ka < 19 ~ 'After'))

cv_tcsa_site_ass_mis_raw <- tcsa_site_ass_mis_raw %>%
  dplyr::group_by(raw_materials_top) %>%
  dplyr::summarize(CV = cv(min_tcsa), count = n()) %>%
  dplyr::rename(sample_size = count)

ggplot(cv_tcsa_site_ass_mis_raw, aes(x = CV, y = sample_size, color = raw_materials_top)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Sample size", title = "CV per each raw material")

ggplot(cv_tcsa_site_ass_mis_raw, aes(x = CV, y = raw_materials_top)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE, color = "red") +
  labs(x = "CV of Min TCSA", y = "Raw Materials", title = "CV per each raw material")
